Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2020-11-25 paper/dcpo_gender_roles.Rmd
fix caption of cs_plot (most recent available year rather than 2020); include year in axis tick label

```{r cs_plot, fig.cap="Egalitarian Gender Attitudes, 2020 \\label{cs_2020}", fig.height=8, warning=FALSE}
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_output.rda"))

@@

p1_data <- theta_results %>%
    group_by(country) %>%
    top_n(1, year) %>%
    ungroup() %>%
    arrange(-mean) %>%
    mutate(half = ntile(mean, 2))

>>>>

```{r cs_plot, fig.cap="Egalitarian Gender Attitudes, Most Recent Available Year \\label{cs_2020}", fig.height=8, warning=FALSE}
load(here::here("data", "dcpo_input_public.rda"))
load(here::here("data", "dcpo_output.rda"))

@@

p1_data <- theta_results %>%
    group_by(country) %>%
    top_n(1, year) %>%
    ungroup() %>%
    arrange(-mean) %>%
    mutate(half = ntile(mean, 2),
           country = paste0(country, " (", year, ")"))
